\documentclass[a4paper,11pt]{article}
\usepackage[pdftex]{graphicx}

\topmargin=0.0in
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\marginparwidth=0.5in

\headheight=0pt
\headsep=0pt
\topmargin=0in
\textheight=9.0in

\begin{document}
\noindent
Zachariah Collins	\hfill CSCI 3308 \\
Alexander Cordero	\hfill Main Project \\
Daniel Strawn		\hfill Software Development Tools and Methods \\

\begin{center}
\LARGE
Fridge Forager
\\
\Large
Project Writeup
\end{center}

\begin{itemize}
\large
\item $\mathbf{1.\ Introduction:}$

\parindent 30pt
The goal of this project was to develop a simple mobile application for the Android platform, the purpose of which is to return possible meal recipes when given one or multiple ingredients as search queries.
\

\item $\mathbf{2.\ Methodologies\ Employed:}$

\parindent 30pt
The following is a brief list of the methodologies used used throughout the development of the app:
\begin{itemize}
\item Peer Code Review
\item Test Driven Development (a lot of it)
\item Remote Development and Collaboration via project tracker and cvs \ldots
\item Agile Development model
\item Pair Programming
\end{itemize}
Rather, we assigned our most experienced java programmer the task of coding, a designer with the task of designing, and a project manager to keep check on everything and direct workflow.

\newpage
\item $\mathbf{3.\ Software\ Tools\ Employed:}$

\parindent 30pt
The following is a brief list of the Software tools and suites used throughout the development of the app.
\begin{itemize}
\item Eclipse IDE with Android SDK plugin
\item Food2Fork API
	\begin{enumerate}
	\item Provided an effective means with which to get recipes when queried with ingredients
	\item Trivializes the neccessity to use an offline or locally created database
	\item Provided experience developing with a third party API
	\end{enumerate}
\item JavaDoc via Eclipse Plugin
	\begin{enumerate}
	\item Changes documented in git repo
	\end{enumerate}
\item LaTeX
	\begin{enumerate}
	\item Used to write this document
	\end{enumerate}
\item Git Content Tracking System hosted via GitHub.com
\item Trello for project management
	\begin{enumerate}
	\item Cross Platform
	\item Android App available
	\item Emailed participants with project updates, changes, and to-dos
	\end{enumerate}
\item Lint Static Analysis
\end{itemize}

\newpage
\item $\mathbf{4.\ Test\ Driven\ Development:}$
\parindent 30pt

The development of our app was handled in concise test cases such that progress was made one small step at a time; never too much too quickly. \
\begin{enumerate}
\item Test Case 0: Basic Test, Compilation (recurring)
	\begin{enumerate}
	\item Code Correctness
		\begin{enumerate}
		\item Is the code syntactically correct?
		\item Does the code correctly call Android functions and classes without error?
		\end{enumerate}
	\end{enumerate}

\item Test Case 1: Assuming previous test passes
	\begin{enumerate}
	\item API usage
		\begin{enumerate}
		\item Does the code correctly call the Food2Fork API?
		\item Does the code correctly pass user-inputted queries to the API?
		\item Does the code correctly parse the JSON returned by the API?
		\end{enumerate}
	\end{enumerate}
\item Test Case 2: (basic functionality) Assuming previous tests pass
	\begin{enumerate}
	\item Running the App in the SDK Emulator
		\begin{enumerate}
		\item Does the app install in the emulator without fail?
		\item Does the app start in the emulator without error?
		\item Are the app's UI elements correctly layed out in the emulator?
		\end{enumerate}
	\item Using the App in the SDK Emulator
		\begin{enumerate}
		\item Does the app accept correctly accept a query in the text field without fail?
		\item Does the app return a list of recipes pertaining to the query entered without fail?
		\item When a recipe is selected, does the app correctly launch the Emulator's default web browser to the webpage containing the recipe without fail?
		\end{enumerate}
	\end{enumerate}
\item Test Case 3: (basic functionality part deux) Assuming previous tests pass
	\begin{enumerate}
	\item Repeat all sub-tests from Test Case 2 on a live Android phone rather than an emulator
	\item Repeat all sub-tests from Test Case 2 on a live Android tablet rather than an emulator
	\end{enumerate}
\item Test Case 4: (minor functionality), Assuming previous tests pass
	\begin{enumerate}
	\item Does the app use the correct display icon?
	\item Does the app rotate correctly if the device's orientation changes without fail?
	\item Does the correctly call third-party web browsers other than the system default without fail?
	\end{enumerate}
\end{enumerate}

\end{itemize}
\end{document}
